\textsf{Are frontier models superhuman chemists?}

### 2024-03-19 src/tex/ms.tex
add main text radar

@@

% GFK performance -> would the models obtain a chemical license 
% Interesting twist perhaps: the performance on the university textbooks or exams is better than on the ones we automatically constructed

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/all_questions_models_completely_correct_radar_human.pdf}
    \caption{\textbf{Performance of the models and humans on the different topics of the \chembench corpus.} The radar plot shows the performance of the models and humans on the different topics of the \chembench corpus. The performance is measured as the fraction of questions that were answered completely correctly by the models.}
    \label{fig:all_questions_models_completely_correct_radar_human}
    \script{analyze_model_reports.py}
\end{figure}

@@

% GFK performance -> would the models obtain a chemical license 
% Interesting twist perhaps: the performance on the university textbooks or exams is better than on the ones we automatically constructed
% in contrast to LLM the human performance is also less spiky
